Cryptanalysis of SBC based post-quantum signature scheme \\\textit{Graduation internship report}

### 2025-07-04 rapport.tex
meilleure complexité mémoire crossbred

	\subsection{Attacks summary}
		\begin{table}[h!]
		\begin{center}
			\begin{tabular}{|c|c|c|c|}
				\hline
				Algorithm & Parameters & Time & Memory \\
				\hline
				Exhaustive search & / & 260 & 24 \\
				\hline
				Dinur First & / & 229 & 200 \\
				\hline
				Dinur Second & / & 221 & 172 \\
				\hline
				Crossbred & D=12, d=10, k=130 & 159 & 90 \\
				\hline
				Naive & / & 150 & 15 \\
				\hline
			\end{tabular}
			\caption{Time and memory complexity of given algorithms in powers of 2.
				For Exhaustive search, Dinur First and Dinur second, the estimations were obtained using CryptographicEstimator \cite{EVZ+24}}
			\label{tab_attacks}
		\end{center}
		\end{table}

@@

	Proof of theorem \ref{EUF-CMA}:
	\begin{proof}
		We model the $SBC$ signature scheme \cite{HJ23} as a 5-round protocol (see Protocol~\ref{Protocol_sig}). By applying Theorem~\ref{theorem_feneu} from \cite{feneu2023}, and under the assumption that the underlying PRG is a $(t_{\mathcal{A}}, \epsilon_{\mathrm{PRG}})$-secure pseudorandom generator, and as established in Lemma~\ref{UB-KOA} that the $SBC$ function is a $(t_{\mathcal{A}}, \epsilon_{\mathrm{OWF}})$-secure one-way function, we conclude that the $SBC$ signature scheme achieves $EUF$-$CMA$ security.
	\end{proof}

>>>>

	\subsection{Attacks summary}
		\begin{table}[h!]
		\begin{center}
			\begin{tabular}{|c|c|c|c|}
				\hline
				Algorithm & Parameters & Time & Memory \\
				\hline
				Exhaustive search & / & 260 & 24 \\
				\hline
				Dinur First & / & 229 & 200 \\
				\hline
				Dinur Second & / & 221 & 172 \\
				\hline
				Crossbred & D=12, d=10, k=130 & 159 & 78 \\
				\hline
				Naive & / & 150 & 15 \\
				\hline
			\end{tabular}
			\caption{Time and memory complexity of given algorithms in powers of 2.
				For Exhaustive search, Dinur First and Dinur second, the estimations were obtained using CryptographicEstimator \cite{EVZ+24}}
			\label{tab_attacks}
		\end{center}
		\end{table}

@@

	Proof of theorem \ref{EUF-CMA}:
	\begin{proof}
		We model the SBC signature scheme \cite{HJ23} as a 5-round protocol (see Protocol~\ref{Protocol_sig}). By applying Theorem~\ref{theorem_feneu} from \cite{feneu2023}, and under the assumption that the underlying PRG is a $(t_{\mathcal{A}}, \epsilon_{\mathrm{PRG}})$-secure pseudorandom generator, and as established in Lemma~\ref{UB-KOA} that the SBC function is a $(t_{\mathcal{A}}, \epsilon_{\mathrm{OWF}})$-secure one-way function, we conclude that the SBC signature scheme achieves $EUF$-$CMA$ security.
	\end{proof}
